### 2016-06-03 filters.tex
updating FP notions to take xplicit distributions for sampling S

In Figure~\ref{fig:fp-notions} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.  In the top notion, the hash functions are secret.  This is the setting addressed by NY, and it capture applications in which the ``hash functions'' are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.  
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.  That is, the adversary does not exploit structural features of the hash functions in its attack.  This notion makes it easy to track the query complexity of an attack.

@@

\if{0}
\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
\label{fig:fp-filter}
\end{figure}
\fi

\tsnote{It might be interesting to run some experiments, e.g. set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.  I quite like the idea of empirically supported/driven crypto.}

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivSecHash{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHashBB{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHash{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

>>>>

In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.  In the top notion, the hash functions are secret.  This is the setting addressed by NY, and it capture applications in which the ``hash functions'' are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.  
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.  That is, the adversary does not exploit structural features of the hash functions in its attack.  This notion makes it easy to track the query complexity of an attack.

For each experiment, we define an associated advantage notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$, distribution~$\distr{U}{n}$ and adversary~$A$, we define:
\begin{align*}
\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
\end{align*}
The probabilities are over the sampling of the set~$S$ and the hash functions $h_1,h_2,\ldots,h_k$, as well as the coins of the adversary.   In all experiments, we track time-complexity~$t$ of~$A$, as well as the number of set-membership ($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In the second, we also track the number of hash-queries $q_{\mathrm{h}}$ that the adversary makes.

@@

%%%%
% \if{0}
% \begin{figure}
% \centering
% \fpage{.6}{
% \hpagess{.6}{.35}
% {
% \experimentv{$\ExpFPSecHash{S,B}{A}$}\\
% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
% $M \gets \Init^{\HashOracle}(S)$\\
% $x \getsr A^{\QryOracle}(S)$\\
% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
% \nudge Ret 1\\
% Ret 0
% }
% %
% {
% \oracle{$\QryOracle(x)$}\\
% Ret $\Qry^{\HashOracle}(M,x)$\\

% \medskip
% \oracle{$\HashOracle(i,x)$}\\
% Ret $h_i(x)$\\
% }
% }
% %%%%%%%
% \fpage{.6}{
% \hpagess{.6}{.35}
% {
% \experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
% $M \gets \Init^{\HashOracle}(S)$\\
% $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
% \nudge Ret 1\\
% Ret 0
% }
% %
% {
% \oracle{$\QryOracle(x)$}\\
% Ret $\Qry^{\HashOracle}(M,x)$\\

% \medskip
% \oracle{$\HashOracle(i,x)$}\\
% Ret $h_i(x)$\\
% }
% }
% %%%%%%%
% \fpage{.6}{
% \hpagess{.6}{.35}
% {
% \experimentv{$\ExpFPPubHash{S,B}{A}$}\\
% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
% $M \gets \Init^{\HashOracle}(S)$\\
% $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
% \nudge Ret 1\\
% Ret 0
% }
% %
% {
% \oracle{$\QryOracle(x)$}\\
% Ret $\Qry^{\HashOracle}(M,x)$\\

% \medskip
% \oracle{$\HashOracle(i,x)$}\\
% Ret $h_i(x)$\\
% }
% }
% \caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
% \label{fig:fp-filter}
% \end{figure}
%\fi
%%%%%

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\
